\documentclass{aer}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{threeparttable}
\usepackage{dcolumn}
\usepackage{hyperref}
\usepackage{url}

\graphicspath{{./figures/}}

\title{Effects of Trade Policy on Economic Growth: Evidence from a Panel of Countries}

\shorttitle{Trade Policy and Economic Growth}

\author{First Author and Second Author}

\abstract{
This paper examines the relationship between trade policy and economic growth
using panel data from 50 countries over the period 1990--2020.
We employ instrumental variables estimation to address endogeneity concerns.
Our results indicate that a one-percentage-point increase in trade openness
is associated with a 0.3 percentage point increase in annual GDP growth.
This effect is robust across different model specifications and sample periods.}

\keywords{trade policy, economic growth, panel data, instrumental variables}

\begin{document}

\maketitle

\section{Introduction}

The relationship between international trade and economic growth has been
a central topic in development economics for decades.

\section{Data and Methodology}

Our dataset covers 50 countries with annual observations from 1990 to 2020.

\subsection{Variable Definitions}

GDP growth rate is measured as the annual percentage change in real GDP per capita.
Trade openness is defined as the sum of exports and imports as a percentage of GDP.

\section{Results}

\begin{table}[ht]
\centering
\caption{Effects of trade openness on economic growth: Panel IV estimates.}
\label{tab:reg}
\begin{threeparttable}
\begin{tabular}{l*{3}{D{.}{.}{2.4}}}
\toprule
 & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} \\
Variable & \mc{1}{c}{Baseline} & \mc{1}{c}{Fixed Effects} & \mc{1}{c}{System GMM} \\
\midrule
Trade Openness & 0.234*** & 0.312*** & 0.289*** \\
               & (0.056)  & (0.078)  & (0.065)  \\
\midrule
Controls & No & Yes & Yes \\
Country FE & No & Yes & Yes \\
Year FE & No & Yes & Yes \\
\midrule
Observations & 1,550 & 1,550 & 1,500 \\
R-squared & 0.12 & 0.34 & 0.41 \\
\end{tabular}
\begin{tablenotes}
\item Standard errors in parentheses. * p $<$ 0.10, ** p $<$ 0.05, *** p $<$ 0.01.
\item Controls include: initial GDP, human capital, infrastructure, institutional quality.
\end{tablenotes}
\end{threeparttable}
\end{table}

\section{Conclusion}

Our findings support the hypothesis that trade openness promotes economic growth,
consistent with theoretical predictions from trade models.

\section*{References}

\begin{thebibliography}{99}
\addtolength{\itemsep}{-0.5ex}
\bibliographystyle{aer}
\bibliography{refs}
\end{thebibliography}

\end{document}
