\section{Introduction}
\label{sec:intro}

Tele-diagnosis for traditional Chinese medicine (TCM) tongue inspection needs repeatable, high-quality images before cloud analytics and electronic medical records integration~\cite{zhang2020tongue,qi2016tongue}.
Clinical diagnosis relies on color, texture, coating, and shape cues that degrade under motion blur, uneven lighting, and incorrect working distance.
Naive pipelines upload every frame, wasting bandwidth on blurred or poorly exposed captures and inflating round-trip time (RTT) on slow links.
\emph{Garbage-in garbage-out} effects are acute: a single blurred upload triggers wasted RTT and may propagate low-confidence features into downstream classifiers.
For RA-L, the robotics question is whether a manipulator-mounted camera can decide \emph{during acquisition} which frames merit upload while preserving a safe control boundary.
Edge-side gating must therefore be (i)~fast for closed-loop capture, (ii)~interpretable for audit, and (iii)~calibratable on real tongue corpora rather than synthetic placeholders alone.

We study a \textbf{cloud--edge--device} stack for a Franka Research~3 (FR3) platform with ROS~2 and MoveIt~\cite{moore2021ros2,chitta2009moveit}.
Perception and routing live in a Python edge gateway (\texttt{franka\_api\_server}) and companion edge modules (\texttt{edge\_iqa}, \texttt{langgraph\_router})---not inside hardware plugins---so algorithms remain testable without a robot.
A lightweight \emph{Edge-IQA} fuses Laplacian sharpness and exposure into $Q_{\mathrm{img}}\in[0,1]$ on COCO tongue ROI crops; a LangGraph router decides \texttt{upload\_cloud}, \texttt{resample\_edge}, or \texttt{fail\_safe} under retry budget $K{=}2$.
An optional learned baseline B3 fine-tunes MobileNetV3-Small on the training split for comparison.

The novelty is the acquisition-time coupling of these pieces, not a standalone IQA score.
Generic NR-IQA predicts perceptual quality after an image exists; generic edge offloading decides where inference runs.
Here the decision changes the robot acquisition loop itself: a rejected tongue ROI triggers a bounded physical resampling action, an accepted ROI avoids unnecessary retries, and an exhausted retry budget enters a fail-safe branch rather than silently uploading poor evidence.
This makes quality assessment an auditable robot policy with timing, safety, and clinical-data boundaries.

We validate on public \textbf{ShezhenV3-COCO} (6{,}719 images with bounding boxes): $\tau$ is calibrated on 572 validation pairs (clear + synthetic blur) with ROI enabled, and the main matrix replays 500 test frames per seed with real Edge-IQA and B3 scores from 553 held-out images.

\textbf{Contributions:} (1)~a robot-acquisition stack that keeps IQA/routing outside the 1\,kHz control loop while exposing HTTP skills for reproducible FR3 capture and recovery;
(2)~a tongue-ROI Edge-IQA gate with $O(HW)$ CPU scoring, interpretable blur/exposure flags, $\tau_{B2}{=}0.465$, and p95 below 10\,ms;
(3)~an auditable LangGraph policy that turns quality scores into bounded upload/resample/fail-safe actions, reducing M1 p50 from 374.0 to 208.3\,ms and raising M2 from 0.560 to 0.604 versus naive upload;
(4)~RA-L-oriented evidence: ShezhenV3 3-seed evaluation, learned B3/B4 alternatives that expose the latency--validity frontier, auxiliary Franka closed-loop trials, and anonymized code/data/video materials.

Section~\ref{sec:related} reviews related work; \S\ref{sec:method}--\ref{sec:experiments} present the method and ShezhenV3 evaluation; \S\ref{sec:conclusion} concludes.
