We presented Edge-IQA and LangGraph confidence-aware routing for robotic TCM tongue-image acquisition on a Franka ROS~2 stack, validated end-to-end on ShezhenV3-COCO (6{,}719 images).
Keeping IQA and routing outside the 1\,kHz control loop preserves real-time safety while enabling JSONL-audited closed-loop policies.
On the held-out test split with real ROI Edge-IQA scores, B2 improves median RTT and valid-frame rate versus naive upload (M1 p50 208.3 vs.\ 374.0\,ms; M2 0.604 vs.\ 0.560) at $\tau_{B2}{=}0.465$; M5 $\rho{\approx}0.36$--$0.47$ characterizes overlap under real tongue texture.
The central contribution is to move image-quality reasoning from post-hoc cloud filtering into the robot acquisition decision itself, with bounded resampling and fail-safe behavior.
The evidence is deliberately layered for a short RA-L format: public-corpus replay provides repeatable statistics, the auxiliary Franka track checks execution-stack feasibility, and the supplementary video/code package documents how the edge policy is invoked on the robot.
This keeps the main claim narrow but verifiable.

\textbf{Limitations.} (1)~Validation and test blur are synthetically injected Gaussian defocus, which may under-represent directional motion smear.
(2)~Edge-IQA overlap between clear and blurred cohorts motivates learned refinement (B3/B4) alongside interpretable B2.
(3)~M2 is scorer-internal; end-to-end clinical validation correlating gating with downstream classifier performance remains future work.
(4)~Three random seeds provide consistent trends; bootstrap CIs in Table~\ref{tab:main-results} support descriptive claims but larger seed budgets would strengthen formal inference.
(5)~Cloud vision and EMR integration remain stubs; M6 confirms execution-stack feasibility but does not replace live clinical deployment data.

\textbf{Future work.} On-device tongue detection for ROI without COCO boxes, Gazebo camera injection, NR-IQA baselines under identical resampling protocols, and multi-center clinical pilots re-calibrating $\tau_{B2}$ on 50+ local sessions before site-specific upload policies.
