% §4.1.1 COCO tongue ROI crop
\subsection{COCO Tongue Region-of-Interest Cropping}
\label{sec:roi}

ShezhenV3-COCO provides axis-aligned bounding boxes for each tongue instance in COCO format $[x,y,w,h]$.
When multiple annotations exist on one frame, we take the union box, expand each side by $8\%$ of width/height (clamped to image bounds), and crop before Edge-IQA resize.
Implementation lives in \texttt{edge\_iqa/coco\_roi.py}; split JSON files store \texttt{bboxes} per image after \texttt{import\_shezhenv3.py}.

\paragraph{Motivation.}
Full-frame scoring includes cheeks, teeth, and background texture that contribute Laplacian energy unrelated to tongue focus.
ROI cropping aligns the quality signal with the anatomical target used by downstream TCM classifiers and reduces sensitivity to out-of-field sharp structures (e.g., lip edges, specular highlights on teeth).

\paragraph{Calibration impact.}
On the full validation split ($n{=}572$ clear images, each paired with synthetic Gaussian blur $r{\in}[2.5,5.0]$, Table~\ref{tab:roi-ablation} compares full-frame vs.\ ROI Edge-IQA.
ROI lowers absolute medians (clear $0.516$ vs.\ $0.564$; blur $0.414$ vs.\ $0.431$) because background high-frequency content is removed.
Minimum-clear minus maximum-blur separation remains negative in both settings ($-0.54$ ROI vs.\ $-0.51$ full-frame), confirming that cohort overlap persists; we therefore report Spearman $\rho$ and routing outcomes rather than assuming separable clusters.
ROI is enabled by default (\texttt{use\_roi: true} in \texttt{tcm\_paths.yaml}) for all ShezhenV3 experiments in this revision.

\begin{table}[t]
\centering
\caption{Edge-IQA calibration: full frame vs.\ COCO tongue ROI (ShezhenV3 val, $n{=}572$ per cohort).}
\label{tab:roi-ablation}
\small
\resizebox{\columnwidth}{!}{%
\begin{tabular}{lcccc}
\hline
Setting & Med.\ clear & Med.\ blur & $\tau$ & Separation \\
\hline
Full frame & 0.564 & 0.431 & 0.498 & $-0.510$ \\
Tongue ROI & 0.516 & 0.414 & 0.465 & $-0.541$ \\
\hline
\end{tabular}%
}
\end{table}

\paragraph{Deployment note.}
When COCO boxes are unavailable at runtime (e.g., a single-camera prototype without detector), Edge-IQA falls back to full-frame scoring by setting \texttt{use\_roi=false}.
The FastAPI gateway accepts optional bbox metadata in future API extensions; offline calibration always uses dataset annotations for reproducibility.
