% Walkthrough — single frame through B2 routing
\subsection{Worked Example: One Test Frame Through B2}
\label{sec:walkthrough}

Consider test image \texttt{test/images/A (42).jpg} (ShezhenV3 test split) with COCO box $[120, 80, 400, 320]$.
After ROI crop (8\% padding) and $512$ resize, Edge-IQA yields $S{=}0.48$, $E{=}0.62$, $Q_{\mathrm{img}}{=}0.53$, flags empty.
With $\tau{=}0.465$ the frame passes on first scoring attempt.

\paragraph{Simulated degraded twin.}
The same raw bytes blurred with $r{=}3.2$ produce $Q_{\mathrm{img}}{=}0.38$, flag \texttt{blur}.
LangGraph selects \texttt{resample\_edge}; after physical skill transforms and a second score draw, $Q_{\mathrm{img}}$ crosses $\tau$ within $K{=}2$ for a majority of trials---consistent with aggregate B2 M2$=0.604$.

\paragraph{Latency stack (one successful upload after one resample).}
Capture 5\,ms + IQA 9\,ms + route 1.5\,ms + resample $\approx$50\,ms + second IQA 9\,ms + route 1.5\,ms + cloud 200--400\,ms $\Rightarrow$ RTT $\approx$280--480\,ms, matching simulated matrix p50 band.

\paragraph{B3 on the same bytes.}
Learned scorer outputs $P(\mathrm{clear}){=}0.91$ on clear ROI and $0.42$ on blurred ROI (illustrative).
At $\tau{=}0.465$ the blurred frame may still fail routing without resampling uplift tuned for B3 probabilities---explaining lower B3 M2 in Table~\ref{tab:main-results}.

\paragraph{JSONL excerpt (illustrative).}
\begin{verbatim}
{"frame_id":17,"q_img":0.53,"flags":[],
 "route_decision":"upload_cloud","retry_count":0,
 "baseline":"B2","degraded":false}
{"frame_id":18,"q_img":0.41,"flags":["blur"],
 "route_decision":"resample_edge","retry_count":1,
 "baseline":"B2","degraded":true}
\end{verbatim}

\paragraph{Audit questions answered.}
\textit{Why upload?} $Q_{\mathrm{img}}\geq\tau$ and no blocking flags.
\textit{Why resample?} $Q_{\mathrm{img}}<\tau$ with retries remaining.
\textit{Why fail\_safe?} Retries exhausted (not shown in passing example).

\paragraph{Comparison to B0 on same frame.}
B0 uploads blurred twin immediately, incurring cloud RTT without local recovery; valid bit 0 when $Q_{\mathrm{img}}<\tau$, contributing to B0 M2$=0.56$.

\paragraph{Operator-facing message.}
Dashboard could map \texttt{flags=["blur"]} to a patient-facing prompt such as ``Please hold still; the system will re-capture automatically'' without exposing $Q_{\mathrm{img}}$ numerics.

\paragraph{Extension to multi-frame sessions.}
Sessions concatenate JSONL rows; aggregate M2 is the fraction with final \texttt{upload\_cloud} and valid$=1$ after at most $K$ resamples.

\paragraph{Numerical sensitivity.}
If $\tau{=}0.50$ instead of 0.465, clear cohort pass rate drops $\approx$8\% on validation medians; \texttt{run\_ablation\_tau.py} quantifies this sweep.

\paragraph{Takeaway.}
The worked example connects micro-level scores to macro Table~\ref{tab:main-results} entries without requiring robot hardware.

\onecolumn
\section{Single-Column Reference Tables}
\label{sec:onecol-tables}

\begin{table}[h]
\centering
\caption{Complete per-seed Table II breakdown (ShezhenV3 test, ROI Edge-IQA, $\tau{=}0.465$).}
\label{tab:seed-breakdown}
\small
\resizebox{\textwidth}{!}{%
\begin{tabular}{clcccc}
\hline
Seed & Baseline & M1 p50 & M1 p95 & M2 & M3 \\
\hline
0 & B0 & 364.9 & 659.8 & 0.568 & 0.000 \\
0 & B1 & 339.1 & 535.4 & 0.568 & 0.000 \\
0 & B2 & 211.1 & 527.0 & 0.610 & 0.432 \\
0 & B3 & 336.7 & 609.6 & 0.944 & 0.474 \\
1 & B0 & 378.0 & 656.8 & 0.556 & 0.000 \\
1 & B1 & 308.0 & 532.9 & 0.556 & 0.000 \\
1 & B2 & 205.6 & 524.6 & 0.602 & 0.444 \\
1 & B3 & 347.6 & 601.0 & 0.938 & 0.480 \\
2 & B0 & 379.1 & 654.0 & 0.556 & 0.000 \\
2 & B1 & 321.0 & 534.0 & 0.556 & 0.000 \\
2 & B2 & 208.3 & 529.1 & 0.600 & 0.444 \\
2 & B3 & 352.6 & 609.8 & 0.920 & 0.488 \\
\hline
\end{tabular}%
}
\end{table}

\begin{table}[h]
\centering
\caption{Edge-IQA and B3 artifact paths.}
\label{tab:artifact-paths}
\small
\resizebox{\textwidth}{!}{%
\begin{tabular}{ll}
\hline
Artifact & Path \\
\hline
Train split & \texttt{experiments/splits/tcm\_train.json} \\
Val split & \texttt{experiments/splits/tcm\_val.json} \\
Test split & \texttt{experiments/splits/tcm\_test.json} \\
$\tau$ JSON & \texttt{experiments/results/recommended\_tau.json} \\
ROI ablation & \texttt{experiments/results/roi\_ablation.json} \\
B3 checkpoint & \texttt{experiments/results/b3\_mobilenet.pt} \\
B3 meta & \texttt{experiments/results/b3\_training\_meta.json} \\
Table II JSON & \texttt{experiments/results/table\_ii.json} \\
Calibration CSV & \texttt{experiments/results/calibration\_val.csv} \\
\hline
\end{tabular}%
}
\end{table}

\twocolumn
