\subsection{Discussion}
\label{sec:discussion}

Table~\ref{tab:main-results} reports \emph{relative} baseline comparison under the documented simulated latency model (\S\ref{sec:setup}); absolute RTT values are not live hospital traces.
B2 reduces M1 p50 from 374.0\,ms (B0) to 208.3\,ms and raises M2 from 0.560 to 0.604 on ShezhenV3 test frames with physical resampling and ROI Edge-IQA ($\tau_{B2}{=}0.465$).
B1 keeps M2 at 0.560 because sub-threshold frames still reach the cloud without closed-loop resampling.
Learned B3/B4 reach M2 $\approx 0.93$--$0.97$ at recalibrated thresholds (Table~\ref{tab:learned-hybrid}; appendix Table~\ref{tab:nr-iqa} for BRISQUE/NIQE-style) with higher edge RTT; the auxiliary Franka track (M6) confirms routing trends without altering Table~\ref{tab:main-results}.
We report descriptive statistics (mean $\pm$ std) over three random seeds; all seeds show B2 outperforming B0 on M1 and M2, while B3/B4 trade higher M1 for higher M2.
Low variance (M2 std $\leq$ 0.007) reflects deterministic test-set scores given a shared frame plan; remaining randomness comes from the latency model and frame-plan shuffling.

COCO tongue ROI (8\% padded union box) aligns scoring with downstream anatomy but does not eliminate clear/blur overlap on Laplacian features (Table~\ref{tab:roi-ablation}, Table~\ref{tab:iqa-calibration}).
Full-frame calibration yields $\tau_{\mathrm{full}}{=}0.498$; the deployed main matrix uses ROI medians $0.516/0.414$, $\tau_{B2}{=}0.465$, and a negative min-clear vs.\ max-blur gap ($-0.541$).
Because ShezhenV3 lacks human blur labels, we inject Gaussian defocus on half of the test frames, mirroring validation calibration; M5 Spearman $\rho{\approx}0.36$--$0.47$ reflects residual overlap under real texture.
B3 (MobileNetV3-Small, 98.3\% val accuracy) achieves M2$=0.934$ at $\tau_{B2}$ versus B2 M2$=0.604$; we retain B2 as the primary deployable path for lowest M1 p50 and auditable \texttt{flags}, while B3/B4 suit higher valid-rate targets with extra edge compute and separate $\tau_{B3}$ calibration.

Edge-IQA and LangGraph are hardware-agnostic: any edge gateway exposing HTTP \texttt{/vision/evaluate} and skill endpoints can replay the same JSONL protocol.
Manual operator retakes resemble \texttt{resample\_edge} but lack consistent $Q_{\mathrm{img}}$ thresholds; Edge-IQA standardizes the decision and exports machine-readable reasons.
Pilot deployment should log JSONL for 50+ sessions, re-calibrate $\tau_{B2}$ locally, and compare cloud classifier confidence before/after routing---without changing downstream diagnosis models in Paper~I scope.
Synthetic blur labels and overlapping score ranges on min-max metrics limit direct clinical claims; see \S\ref{sec:failure-cases} for failure modes and B3/$\tau$ scale coupling.
All scoring runs offline on a public research corpus; no patient identifiers are written to JSONL logs.
Splits and scripts are in the repository; implementations live in \texttt{doctor/paper1/edge\_iqa/}, \texttt{langgraph\_router/}, and \texttt{franka\_api\_server/}.
Paper~I argues for a \emph{routing architecture} validated on real TCM imagery, not for a new SOTA IQA regressor.

The results form a deployment trade-off.
B0 spends cloud RTT on frames that could have been repaired locally, whereas B1 saves some upload time but cannot improve frame validity without a physical recovery action.
B2 is the smallest policy that changes both latency and input quality; B3/B4 quantify the additional valid-frame rate available when a site accepts learned-model maintenance and higher edge RTT.

M2 (valid-frame rate) is an internal metric: it measures the proportion of frames passing the Edge-IQA or learned threshold, not an independent quality annotation.
We report M2 as a proxy for the routing policy's discrimination ability rather than a direct measure of clinical image quality; future work should correlate M2 with downstream classifier confidence on accepted vs.\ rejected frames.
A larger seed budget or bootstrap confidence intervals would strengthen formal inference beyond the consistent descriptive trends shown here.
