\section{Implementation Details}
\label{sec:implementation}

This section documents the edge gateway surface and offline experiment drivers used for ShezhenV3 full validation, enabling third-party replication without reading the entire monorepo.

\subsection{Edge Gateway API}
Table~\ref{tab:api-endpoints} lists Paper~I HTTP endpoints implemented in \texttt{franka\_api\_server}; all require header \texttt{X-API-Key} when authentication is enabled.

\begin{table}[t]
\centering
\caption{Edge gateway endpoints (Paper~I).}
\label{tab:api-endpoints}
\small
\resizebox{\columnwidth}{!}{%
\begin{tabular}{llp{0.36\linewidth}}
\hline
Method & Path & Purpose \\
\hline
POST & \texttt{/api/v1/vision/evaluate} & Edge-IQA on upload \\
POST & \texttt{/api/v1/motion/skills/go\_to\_tongue\_pose} & Tongue skill \\
POST & \texttt{/api/v1/motion/skills/go\_to\_face\_pose} & Face skill \\
POST & \texttt{/api/v1/motion/move\_joints} & Joint PTP \\
GET & \texttt{/api/v1/status/joints} & Joint snapshot \\
\hline
\end{tabular}%
}
\end{table}

\paragraph{Vision evaluate contract.}
The gateway forwards uploads to \texttt{python -m edge\_iqa.cli --json} with \texttt{PYTHONPATH} pointing to \texttt{doctor/paper1}.
Response fields include \texttt{q\_img}, \texttt{flags}, \texttt{t\_iqa\_ms}, and \texttt{threshold\_tau} loaded from \texttt{recommended\_tau.json} when present.
Subprocess isolation prevents NumPy/PIL work from blocking the \texttt{rclpy} executor thread.

\subsection{Environment and Configuration}
Table~\ref{tab:env-vars} summarizes environment variables; Paper~I experiments set \texttt{PAPER1\_MODE=1} to disable impedance/collision routes unrelated to acquisition.

\begin{table}[t]
\centering
\caption{Selected environment variables (\texttt{franka\_api\_server}).}
\label{tab:env-vars}
\small
\resizebox{\columnwidth}{!}{%
\begin{tabular}{llp{0.34\linewidth}}
\hline
Variable & Default & Role \\
\hline
\texttt{PAPER1\_ROOT} & \texttt{doctor/paper1} & IQA + LangGraph \\
\texttt{PAPER1\_MODE} & \texttt{false} & Disable controller \\
\texttt{PAPER1\_IQA\_SUBPROCESS} & \texttt{true} & Subprocess scorer \\
\texttt{PAPER1\_VISION\_THRESHOLD\_TAU} & 0.55 & Fallback $\tau$ \\
\texttt{FRANKA\_API\_PORT} & 8000 & Listen port \\
\hline
\end{tabular}%
}
\end{table}

\subsection{Offline Experiment Drivers}
ShezhenV3 validation executes in order: (1)~\texttt{import\_shezhenv3.py} writes \texttt{experiments/splits/tcm\_\{train,val,test\}.json} with \texttt{bboxes} per image; (2)~\texttt{train\_b3\_mobilenet.py} (optional, PyTorch in \texttt{.venv}) writes \texttt{b3\_mobilenet.pt}; (3)~\texttt{calibrate\_tau\_tcm.py} scores ROI validation pairs; (4)~\texttt{roi\_ablation.py} compares full vs.\ ROI; (5)~\texttt{run\_matrix\_tcm.py} replays test frames for B0--B3 using Edge-IQA (B2) and \texttt{learned\_b3.py} (B3); (6) figure/table builders regenerate \LaTeX{} snippets.
The orchestrator \texttt{scripts/paper1\_run\_tcm\_full.sh} chains these steps and invokes \texttt{paper1\_build\_draft.sh}.

\subsection{ROI and B3 Modules}
\texttt{edge\_iqa/coco\_roi.py} implements union-box crop with fractional padding.
\texttt{scorer.py} accepts \texttt{bboxes}, \texttt{use\_roi}, and \texttt{roi\_padding} kwargs shared by calibration and gateway subprocess calls.
\texttt{learned\_b3.py} loads \texttt{b3\_mobilenet.pt}, applies the same ROI crop, and returns $P(\mathrm{clear})$ as $Q_{\mathrm{img}}$ for B3 matrix rows.

\paragraph{Import pipeline details.}
COCO \texttt{train.json}/\texttt{val.json}/\texttt{test.json} annotations are grouped by \texttt{image\_id}; each split entry stores absolute \texttt{path}, relative \texttt{rel\_path}, and a list of \texttt{bboxes}.
Images without annotations still import but ROI falls back to full frame.

\paragraph{B3 training runtime.}
Full train (5594 images, 5 epochs, batch 64) completes in approximately 45 minutes on a laptop CPU reading from WSL-mounted storage; validation accuracy 98.34\% on 1144 ROI pairs.
GPU acceleration is optional when CUDA drivers match the installed PyTorch build.

\paragraph{Matrix scoring split.}
For each test frame, \texttt{run\_matrix\_tcm.py} precomputes both \texttt{q\_b2} (Edge-IQA) and \texttt{q\_b3} (learned) once per frame plan, then simulates baselines B0--B1 with B2 scores, B2 with B2 scores, and B3 with B3 scores---avoiding double-counting resampling uplift across baselines.

\paragraph{Repository layout (Paper~I relevant).}
\begin{verbatim}
doctor/paper1/
  edge_iqa/          scorer, coco_roi, learned_b3, cli
  langgraph_router/  route(), graph nodes
  experiments/
    splits/          tcm_*.json
    results/         tau, tables, b3 checkpoint
    edge_iqa/        calibrate, train, roi_ablation
  latex/             main.tex, sections/
franka_api_server/   FastAPI gateway
\end{verbatim}

\paragraph{Continuous integration scope.}
CI runs unit tests without the multi-gigabyte TCM mount; full ShezhenV3 validation remains a local manuscript target documented in \texttt{REPRODUCE.md}.

\paragraph{Versioning checklist.}
When updating ROI padding or Edge-IQA weights, bump a \texttt{calibration\_version} field in \texttt{recommended\_tau.json} (manual) and re-run the full orchestrator before updating Table~\ref{tab:main-results}.

\paragraph{Dataset path mapping.}
Windows path \texttt{D:\textbackslash BaiduNetdiskDownload\textbackslash shezhenv3-coco\textbackslash shezhenv3-coco} maps to WSL \texttt{/mnt/d/BaiduNetdiskDownload/shezhenv3-coco/shezhenv3-coco} in \texttt{tcm\_paths.yaml}; other mount points only require updating \texttt{dataset\_root}.

\paragraph{Unit tests.}
\texttt{edge\_iqa/tests/test\_scorer.py} checks clear/blur separation on synthetic images; \texttt{tests/test\_routing.py} covers all routing branches.
Continuous integration can run these without the multi-gigabyte TCM mount, while full validation remains an optional local target for manuscript updates.
